\paperTitle

### 2014-02-19 doc/icml2014/directed.tex
Updated appendix a bit:

Note that in each of the above cases,
  for any clique $\sC$, each hidden variable $h_i \in \sC$ has its own
  view which is conditionally independent given the other hidden variables in
  the clique.
%Fundamentally, algorithm takes advantage of having a view for every
  %hidden variable in a clique to help identify its hidden state.
We capture this general property as follows:
\begin{property}(Exclusive views)
  \label{prop:exclusive-views}
A hidden sub-graph $\sG' \subseteq \sG$ (typically a clique $\sC \in
  \sG$) is said to possess the \textbf{exclusive views property} if for
  every hidden variable $h_i \in \sG'$, there is some observed variable,
  $x_{v}$, which is conditionally independent of the rest of the clique
  given $h_i$, and whose conditional moment $\mOpp{v}{i} \eqdef
  \Pr(x_{v} \mid h_i)$ can be estimated consistently.
We call $x_v$ the exclusive view of $h_i$ in $\sG'$.
\end{property}

@@

\begin{lemma}[Bottlenecks guarantee exclusive views]
  \label{lem:bottleneck-views}  
Let $\sG' = \{ h_{i_1}, \cdots, h_{i_m} \} \subseteq \sG$ be
  a connected sub-graph of hidden variables. If every hidden variable
  $h_i \in \sG'$ is a bottleneck, then they each have an exclusive view.
\end{lemma}
\begin{proof}
  By \lemmaref{reduction}, we can assume that every observed
  variable is a leaf in the graph, causing any v-structures in the graph
  to be active. This allows us to reason about independence simply by
  checking whether or not two nodes are connected or not. Note that this
  proof applies for undirected graphs as well.

@@

  Thus, it must be the case that $\sV_{h} \subsetneq \Union_{h' \neq
    h \in \sC} \sV_{h'}$ and hence there exists a unique view for $h$.

  Algorithmically, finding the unique view for $h$ can be done by
  subtracting the views of all other variables in the sub-graph from
  $\sV_h$,i.e. $x_{v_h} \in \sV_h \setminus \Union_{h' \in \sC} \sV_{h'}$
\end{proof}

>>>>

Note that in each of the above cases,
  for any clique $\sC$, each hidden variable $h_i \in \sC$ has its own
  view which is conditionally independent given the other hidden variables in
  the clique.
%Fundamentally, algorithm takes advantage of having a view for every
  %hidden variable in a clique to help identify its hidden state.
We capture this general property as follows:
\begin{property}(Exclusive views)
  \label{prop:exclusive-views}
A hidden clique $\sC \in \sG$ is said to possess the \textbf{exclusive views property} if for
  every hidden variable $h_i \in \sC$, there is some observed variable,
  $x_{v}$, which is conditionally independent of the rest of the clique
  given $h_i$, and whose conditional moment $\mOpp{v}{i} \eqdef
  \Pr(x_{v} \mid h_i)$ can be estimated consistently.
We call $x_v$ the exclusive view of $h_i$ in $\sC$.

This property also extends to any connected sub-graph $\sG' \in \sG$.
\end{property}

@@

\begin{lemma}[Bottlenecks guarantee exclusive views]
  \label{lem:bottleneck-views}  
Let $\sG' = \{ h_{i_1}, \cdots, h_{i_m} \} \subseteq \sG$ be
  a connected sub-graph of hidden variables. If every hidden variable
  $h_i \in \sG'$ is a bottleneck, then they have an exclusive view.
\end{lemma}
\begin{proof}
  By \lemmaref{reduction}, we can assume that every observed
  variable is a leaf in the graph, causing any v-structures in the graph
  to be active. This allows us to reason about independence simply by
  checking whether or not two nodes are connected or not. Note that this
  proof applies for undirected graphs as well.

@@

  Thus, it must be the case that $\sV_{h} \subsetneq \Union_{h' \neq
    h \in \sG'} \sV_{h'}$ and hence there exists a unique view for $h$.

  Algorithmically, finding the unique view for $h$ can be done by
  subtracting the views of all other variables in the sub-graph from
  $\sV_h$,i.e. $x_{v_h} \in \sV_h \setminus \Union_{h' \in \sG'} \sV_{h'}$
\end{proof}
